\section{Compiling Tachyon From Source Code}
\index{compiling on Unix systems}
  In order to use Tachyon, particularly on distributed memory
parallel computers, you may need to compile it from source code.
Compilation of Tachyon is a fairly straightforward process.  
Once the Tachyon distribution has been downloaded from the 
web site, unpack the distribution using gunzip and tar.
Once the distribution is unpacked, change directory into the 
'tachyon' subdirectory, and then into the 'unix' directory.  
Once in the 'unix' directory, type {\tt make} to see the list of 
configurations that are currently supported.
To compile Tachyon for most platform targets, one need only run 
{\tt make platform-name-string}.  The resulting
Tachyon executable and library files are contained within a 
subdirectory of the 'tachyon/compile' directory, named to match
the compilation target.

Hopefully once you've run 'make' to build Tachyon, 
everything went well and you now have a binary to run.  If you are building
a version that uses MPI, OpenGL, or other special features,
you may need to edit the {\tt Make-config} file to edit the 
locations of libraries and header files needed for compilation.
If you have trouble, for now the best way to go is to send me email, at
{\em \EMAIL}  As I have time, I plan to improve this document and provide
more detailed instructions on compilation.

\begin{figure}[tb]
\begin{center}
%        xleftmargin=0pt,
%        xrightmargin=0pt
\lstset{numbers=none,
        frame=lines,
        basicstyle=\small,
        language={},
        commentstyle=\color{blue},
        }
\begin{lstlisting}
johns:/tmp % gunzip tachyon.tar.gz
johns:/tmp % tar -xvf tachyon.tar.gz
johns:/tmp % cd tachyon
johns:/tmp/tachyon % cd unix
johns:/tmp/tachyon/unix % make
  Choose one of the architectures specified below.
----------------------------------------------------
              Parallel Versions        

    linux-mpi - Linux            Generic MPI           
    linux-thr - Linux            POSIX Threads          

[... Trimmed for brevity ...]

        clean - Remove .o .a and executables
---------------------------------------------------
Type 'make arch' to build a target listed above.

johns:/tmp/tachyon/unix % make linux-thr
\end{lstlisting}
\end{center}
 \caption{Example Tachyon compilation steps.}
 \label{fig:perspcamera}
\end{figure}

