\section{Introduction}
Tachyon is designed to be a very fast renderer, based on ray tracing,
and employing parallel processing to achieve high performance.

At the present time, Tachyon and its scene description language are fairly
primitive, this will be remedied as time passes.  For now I'm going to 
skip the ``intro to ray tracing'' and related things that should probably 
go here, they are better addressed by the numerous books on the subject
written by others.  This document is designed to serve the needs of 
sophisticated users that are already experienced with ray tracing
and basic graphics concepts, rather than catering to beginners.  
If you have suggestions for improving this manual, I'll be glad 
to address them as time permits.

Until this document is finished and all-inclusive, the best way to 
learn how Tachyon works is to examine some of the sample scenes that 
I've included in the Tachyon distribution.  Although they are all very 
simple, each of the scenes tries to show something slightly 
different Tachyon can do.  Since Tachyon is rapidly changing to accommodate 
new rendering primitives and speed optimizations, the scene 
description language is likely to change to some degree as well. 

\subsection{Tachyon Feature List}
  Although Tachyon is a very small program, it is relatively 
complete and even has a few features often associated with 
much larger and more sophisticated ray tracing packages:

\begin{itemize}
\item Parallel execution using MPI, POSIX threads, Unix-International threads,
      or Microsoft Windows threading APIs
\item Run-time display and interactive ray tracing
      (on sufficiently fast systems) with built-in support
      for Spaceball and SpaceNavigator 6DOF motion controllers for
      fly-through navigation
\item Ambient occlusion lighting
\item Support for 48-bit deep color image formats
\item Supersampled antialiasing
\item Linear, exponential, and exponential-squared fog
\item Perspective, orthographic, and depth-of-field camera projection
      modes, with eye-space frustum controls
\item Positional, directional, and spot lights, with optional attenuation.
\item Provides commonly used geometric objects including 
      Spheres, Planes, Triangles, Cylinders, Quadrics, and Rings
\item Texture mapping (both texture images, and volumetric textures), 
      with automatic MIP-map generation.
\item Direct rendering of volumetric data
\item Support for angle-modulated transparency, 
      limited-ray-depth transparency, edge cueing with outline shading,
      and other special shading modes useful for molecular visualization
\item Grid-based spatial decomposition for effecient rendering of both
      static and time-varying geometry
\end{itemize}


